Topological Equivariant Artist Model

### 2022-03-02 slides/main.tex
artist equiv

            \onslide*<0|handout:3>{\underbrace{\opensetc\times[0,1]^{m}}_{\opensetgc}}

@@

\subsection{Equivariance}

\begin{frame}<presentation:1|handout:1>{Transform Data}
    \begin{block}{Fiber Bundle Category}
        \begin{description}[style=newline]
            \item[object] $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item[morphisms] $\dfuncc: \dtotalc \rightarrow \dtotalc^{\prime}$
        \end{description}
    \end{block}
    \begin{block}{Fiber Category}
        The fiber $\dfiberc$ is a  monoidal category (single object w/ bicartesian product operator on category) of an arbitrary type $\mathcal{C}$. The morphisms on the fiber are $Hom(\dfiberc, \dfiberc)$
    \end{block}

@@

\begin{frame}<presentation:1|handout:1>{Equivariant Artist}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \sheafc_{\dbasec, \dtotalc} 
            \arrow[r, "\vartistc", Rightarrow, color=artist] 
            \arrow[d, "\dfuncc_{\dtotalc}"', color=action] \& 
            \sheafc_{\gbasec, \gtotalc} 
            \arrow[d, "\dfuncc_{\gtotalc}", color=action, dashed] \\
            \sheafc_{\dbasec^{\prime}, \dfuncpullc\dtotalc} 
            \arrow[r, "\vartistc", Rightarrow, color=artist]\& 
            \sheafc_{\gbasec^{\prime},\dfuncpullc\gtotalc}
        \end{tikzcd} 
        \end{equation*}

    \begin{alertblock}{Artist Constraints}
        \begin{align*}
            \vartistc(\dsectionc^{a}) = \vartistc(\dsectionc^{b}) &\centernot\implies \dsectionc^a = \dsectionc^b \\
            \vartistc(\dsectionc^{a})  = \vartistc(\dsectionc^{b}) &\implies \vartistc(\dfuncc_{\dtotalc}(\dsectionc^{a})) = \vartistc(\dfuncc_{\dtotalc}(\dsectionc^{b}))
        \end{align*}
    \end{alertblock}
\end{frame}

\begin{frame}<presentation:1|handout:1>{Equivariant $\dfunchc$}
    \note{Maybe move to implementation section}
        \begin{equation*}
            \begin{tikzcd}[ampersand replacement=\&]
            \opensetgc 
            \arrow[rr, "\vindexc", color=functor] 
            \arrow[dd, "\dfunchc_{\gbasec}"', dashed, color=action] 
            \&  \& 
            \opensetc 
            \arrow[dd, "\dfunchc_{\dbasec}", color=action] \\
            \&  \& \\
            \opensetgc^{\prime} 
            \arrow[rr, "\vindexc"', color=functor]
            \&  \& 
            \opensetc^{\prime}\\
            \underbrace{\dbasec \times {[0,1]}^{m}}_{\gbasec} \arrow[rr,"\vindex", maps to, color=functor] \& \& \dbasec
            \end{tikzcd}
        \end{equation*}
\end{frame}

>>>>

            \onslide*<0|handout:3>{\overbrace{\opensetc\times[0,1]^{m}}^{\opensetgc}}

@@

\subsection{Equivariance}
\begin{frame}<presentation:1|handout:1>{Transform Data}
    \begin{block}{Fiber Bundle Category}
        \begin{description}[style=newline]
            \item[object] $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item[morphisms] $\dfuncc: \dtotalc \rightarrow \dtotalc^{\prime}$
        \end{description}
    \end{block}
    \begin{block}{Fiber Category}
        The fiber $\dfiberc$ is a  monoidal category (single object w/ bicartesian product operator on category) of an arbitrary type $\mathcal{C}$. The morphisms on the fiber are $Hom(\dfiberc, \dfiberc)$
    \end{block}

@@

\begin{frame}<presentation:1|handout:1>{Equivariant Artist}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
        \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
        \arrow[rrr, "\vartistc", Rightarrow, color=artist] 
        \arrow[d, "\dfuncpullc_{\dtotalc}"', color=action] 
        \& \& \& 
        \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
        \arrow[d, "\dfuncpullc_{\gtotalc}", dotted] \\
        \cgamma{\opensetc^{\prime}}{\dfuncpullc_{\dtotalc}\dtotalc\restriction_{\opensetc^{\prime}}} 
        \arrow[dd, "\dfunctc_{\dtotalc}"', color=action] \& 
        \opensetc 
        \arrow[lu, dashed, maps to, color=sheaf] \& 
        \opensetgc 
        \arrow[l, "\vindexc"', color=functor] 
        \arrow[ru, dashed, maps to, color=sheaf] \& 
        \cgamma{\opensetgc^{\prime}}{\dfuncpullc_{\gtotalc}\gtotalc\restriction_{\opensetgc^{\prime}}} 
        \arrow[dd, "\dfunctc_{\gtotalc}", dotted, color=action] \\
        \& 
        \opensetc^{\prime} 
        \arrow[u, "\dfunchc_{\dtotalc}", color=action] 
        \arrow[ld, dashed, maps to, color=sheaf] 
        \arrow[lu, dashed, maps to, color=sheaf] \& 
        \opensetgc^{\prime} 
        \arrow[l, "\vindexc"', color=functor] 
        \arrow[u, "\dfunchc_{\gtotalc}"', dotted, color=action] 
        \arrow[rd, dashed, maps to, color=sheaf] 
        \arrow[ru, dashed, maps to, color=sheaf] \& \\
        \cgamma{\opensetc^{\prime}}{\dtotalc^{\prime}\restriction_{\opensetc^{\prime}}} 
        \arrow[rrr, "\vartistc^{\prime}", Rightarrow, color=artist]  
        \& \& \& 
        \cgamma{\opensetgc^{\prime}}{\gtotalc^{\prime}\restriction_{\opensetgc^{\prime}}}
        \end{tikzcd}
    \end{equation*}
        $(\vartistc, \vartistc^{\prime})$ are equivariant with respect to $\dfuncc_{\dtotalc}$ if a compatible transform  $\dfuncc_{\dtotalc}$ can be defined such that 
        \begin{equation*}
            \vartistc^{\prime}(\dfunctc_{\dtotalc}(\dsectionc(\dfunchc_{\dtotalc}(\vindexc(\gbasepointc^{\prime}))))) = \dfunctc_{\gtotalc}(\vartistc(\dsectionc(\vindexc(\dfunchc_{\gtotalc}(\gbasepointc^{\prime})))))
        \end{equation*}
        for all points$
        \gbasepointc^{\prime}\in \gbasec^{\prime$
\end{frame}

\begin{frame}<presentation:0|handout:0>{$\vartistc= \vartistc^{\prime}$}
    \begin{align*}
        \vartistc(\dsectionc^{a}) = \vartistc(\dsectionc^{b}) &\centernot\implies \dsectionc^a = \dsectionc^b \\
        \vartistc(\dsectionc^{a})  = \vartistc(\dsectionc^{b}) &\implies \vartistc(\dfuncc_{\dtotalc}(\dsectionc^{a})) = \vartistc(\dfuncc_{\dtotalc}(\dsectionc^{b}))
    \end{align*}
\end{frame}
